---
title: "Goal Programming"
author: "Karthik Badiganti"
date: "2022-11-06"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Given Equation

```{r given table}
library(lpSolveAPI)

gp_table <- matrix(c("Total Profit", "Employment Level", "Earnings Next Year",
20,6,8,
15,4,7,
25,5,5,
"Maximize","=50",">=75", "Millions of Dollars", "Hundreds of Employees", "Millions of Dollars"), ncol=6)
colnames(gp_table) <- c("Factor","Product 1", "Product 2", "Product 3", "Goal", "Units")
print(gp_table)
```

## Formulating Goal programming equation

```{r goal programming}

gp <- read.lp("goal.lp")
gp
```

## Solving GP

```{r}
solve(gp)

get.objective(gp)
get.variables(gp)

```

1.  **Interpretation:** After applying simplex method we get x1=0, x2=0, x3=15 , y1p=25, y1m=0, y2m=0, y2p=0

2.  From the above we can interpret that product 3 can be optimized by increasing 15 units which maximizes profit.

3.  since y2m=0, the goal for earnings has been achieved. But the employment goal has been exceeded by 25(2500 employees) in order to maximize the objective function.

4.  The maximized objective of the company is 225
