---
title: "QMM FINAL PROJECT"
author: "Group 1"
date: "2022-12-09"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Random data Creation

```{r data}
library(randomNames)
set.seed(12345)
GPA <- sample(1:4, 12,replace = TRUE)


Experience<-sample(0:6, 12,replace = TRUE)

Presentation_skills<-sample(1:10, 12,replace = TRUE)
Students<-c(1,2,3,4,5,6,7,8,9,10,11,12)
```

Here success of student is assumed to be **success=(0.5\*GPA+0.3\*Experience+0.2\*Presentation_skills)**

## Created Data

```{r given data}
set.seed(12345)
student_data<-data.frame(Students,GPA,Experience,Presentation_skills)

student_data$success<-with(student_data,0.5*GPA+0.3*Experience+0.2*Presentation_skills)

student_data
```

**Constraints and Assumptions used:**

-   Since we need 4 groups with equal success, our objective is to maximize one group success and apply a constraint where all groups success ratio is equal.

-   Each group can have only 3 members.

-   Total GPA of group should be atleast 5

-   Total Experience of group should be atleast 5

-   Total Skill rating of group should be atleast 11

-   Assuming all decision variables are binary

## Importing LP File

```{r lp import}

library(lpSolveAPI)
y <-read.lp("GA_DATA.lp")
print(y)

```

**We can see that there are 48 decision variables with 31 constraints in the LP model**

**Decision Variables= X~ij~ **

**where i= 1,2,3,4 Groups**

**j=1,2,3,4,5,6,7,8,9,10,11,12 Students**

## Solving LP

```{r lpsolving}
set.seed(2345)
solve(y)

Assignment <- get.variables(y)
```

## Output after solving LP

```{r}
# Objective maximisation
get.objective(y)

# Constraints
get.constraints(y)

#decision variables
a<-matrix(Assignment,nrow=12,byrow=F)
colnames(a)<-c('Group 1','Group 2','Group 3','Group 4')
rownames(a)<-student_data$Students
a
```

-   **Group1 students - 4,7,12**

-   **Group2 Students - 2,3,9**

-   **Group3 Students - 5,8,10**

-   **Group4 Students - 1,6,11**
