---
title: "Integer Programming"
author: "Karthik Badiganti"
date: "2022-11-20"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

## Loading Packages

```{r packages}
library(lpSolveAPI)
```

## Loading IP Equation

```{r equation}
ip <- read.lp("AP.lp")
print(ip)
```

Here x1,x2, x3, x4, x5, x6, x7 are the number of workers assigned to shifts

## Given Table

```{r given table}

# Day wise workers required
ap_workers_required <- matrix(c("Sunday","Monday","Tuesday","Wednesday"
                                ,"Thursday","Friday","Saturday",
                       18,27,22,26,25,21,19),ncol=2,byrow = F)
colnames(ap_workers_required) <- c("Day of the week", "Workers Required")
as.table(ap_workers_required)

# Day offs for workers

Day_offs <- matrix(c(1,2,3,4,5,6,7,
"Sunday and Monday","Monday and Tuesday","Tuesday and Wednesday",
"Wednesday and Thursday","Thursday and Friday",
"Friday and Saturday","Saturday and Sunday",
"$775","$800","$800","$800","$800","$775","$750"),ncol=3,byrow=F)
colnames(Day_offs) <- c("Shift", "Days Off", "Wage")
as.table(Day_offs)

```

## Solving lp

```{r solving lp}
set.seed(1234)
solve(ip)
get.objective(ip)
s<-get.variables(ip)
s
```

From the above we can observe that,

The total cost is the objective function value, which is **\$25675.**

Also **x1=2, x2=4, x3=5, x4=0, x5=8, x6=1, x7=13**

Also number of workers available on each day are,

**Sunday:** x2 + x3 + x4 + x5 + x6  = **18 workers**

**Monday:** x3 + x4 + x5 + x6 + x7 = **27 workers**

**Tuesday:** x1+x4 + x5 + x6 + x7=  **24 workers**

**Wednesday:** x1 + x2+ x5 + x6 + x7 =  **28 workers**

**Thursday:** x1 + x2 + x3+ x6 + x7 =  **25 workers**

**Friday:** x1 + x2 + x3 + x4+ x7 = **24** **workers**

**Saturday:** x1 + x2 + x3 + x4 + x5 = 5+1+5+0+8 = **19** **workers**
